BIP32-Ed25519++: A More Secure Hierarchical Deterministic Wallet Standard for Ed25519 Keys

### 2024-06-13 paper.tex
citation sort, title, author
remove cite from author line
touch up abstract

\title{Bip32-Ed25519++: A More Secure Hierarchical Deterministic Wallet Standard for Ed25519 Keys}

% \author{Chris Peikert\cite{ChrisP}}

@@

\twocolumn[
  \begin{@twocolumnfalse}
    \maketitle
    \begin{abstract}
      \abstractText
      Implementing BIP32-style HD wallets for Ed25519 keys is a non-trivial task due to the non-linear key space of Ed25519. The paper BIP32-Ed25519 Hierarchical Deterministic Keys over a Non-linear Keyspace has seen adoption in the industry, but has some security issues. In this paper modifications are proposed that addresses those issues, at the cost of reducing the number of possible levels of child keys.
      \newline
      \newline
    \end{abstract}
  \end{@twocolumnfalse}
]

@@

\nocite{*}
\bibliographystyle{plain}
\bibliography{sources}

>>>>

\title{BIP32-Ed25519++: A More Secure Hierarchical Deterministic Wallet Standard for Ed25519 Keys}

\author{Chris Peikert}

@@

\twocolumn[
  \begin{@twocolumnfalse}
    \maketitle
    \begin{abstract}
      \abstractText Implementing BIP32-style Hierarchical Deterministic (HD) wallets for Ed25519 keys is a non-trivial task, due to the non-linear key space of Ed25519.
      A proposal by Khovratovich and Law has seen adoption in the industry, but it has some security issues.
      This paper proposes some small modifications that address those issues, at the cost of reducing the number of levels in the hierarchy.
      \newline \newline
    \end{abstract}
  \end{@twocolumnfalse}
]

@@

\nocite{*}
\bibliographystyle{unsrt}
\bibliography{sources}
